Compilation and Backend-Independent Vectorization for Multi-Party Computation

### 2022-05-25 overleaf/tech_report/prob_stmt_np_hardness.tex

where $L_\alpha$ is the number of $\alpha$-instructions and $L_\beta$ is the number of $\beta$ ones.
(We used this formula to compute the cost of the unrolled MPC Source program in~\secref{sec:overview}.)
%$cost(S_i) = \alpha$ or $\beta$. if $S_i$ is an $A$-instruction and $cost(S_i) = \beta$ if $S_i$ is an $M$-instruction. 
The cost of $P$ is more interesting:

@@

Our goal is to construct a parallel schedule $P$ that reduces the program cost (when compared to cost of $S$), possibly an optimal schedule. 
Originally we hoped that the problem is simper and computation of the optimal schedule was tractable. Unfortunately, the optimal schedule turns out to be NP-hard via a reduction 
to the Shortest Common Supersequence problem.

@@

%The problem of finding a schedule $P$ with a minimal $cost(P)$ is shown to be NP-Hard problem, as it can be reduced to the problem of finding a \emph{shortest common supersequence}, a known NP-Hard problem~\cite{Vazirani:2010}. 
The shortest common supersequence problem~\cite{Vazirani:2010} is as follows: {\it given two or more sequences find the shortest sequence that contains all of the original sequences.} This can be solved in $O(n^k)$ time, where $n$ is the cardinality of the longest sequence and $k$ is the number of sequences. %For our problem $n$ is the maximum length of a sequence and $k$ is the number of instructions of sequences. 
We can see that the optimal schedule is the shortest schedule, since the shortest schedule minimizes the fixed cost while the variable cost remains the same.

>>>>

where $L_\alpha$ is the number of $\alpha$-instructions and $L_\beta$ is the number of $\beta$ ones.
(We used this formula to compute the cost of the unrolled MPC Source program in~\secref{sec:overview}.)
%$cost(S_i) = \alpha$ or $\beta$. if $S_i$ is an $A$-instruction and $cost(S_i) = \beta$ if $S_i$ is an $M$-instruction. 
The cost of schedule $P$ is more interesting:

@@

Our goal is to construct a parallel schedule $P$ that reduces the program cost (when compared to cost of $S$), possibly an optimal schedule. 
Originally we hoped that the problem is simper and computation of the optimal schedule is tractable. Unfortunately, the optimal schedule turns out to be NP-hard via a reduction 
to the Shortest Common Supersequence problem.

@@

The problem of finding a schedule $P$ with a minimal $cost(P)$ is shown to be NP-Hard problem, as it can be reduced to the problem of finding a \emph{shortest common supersequence}, a known NP-Hard problem~\cite{Vazirani:2010}. The shortest common supersequence problem is as follows: {\it given two or more sequences find the the shortest sequence that contains all of the original sequences.} This can be solved in $O(n^k)$ time, where $n$ is the cardinality of the longest sequence and $k$ is the number of sequences. %For our problem $n$ is the maximum length of a sequence and $k$ is the number of instructions of sequences. 
We can see that the optimal schedule is the shortest schedule, since the shortest schedule minimizes the fixed cost while the variable cost remains the same.
